`mathml`: Translate R Expressions to MathML and LaTeX

### 2023-06-20 rj/mathml.Rmd
Small changes in the text (references added)

As it can be seen from the output, to the variable `term` is not assigned the 
result of the calculation, yet an R\ call [see, e.g., @Wickham2019, for details 
on "non-standard evaluation"], which can eventually be evaluated with `eval()`.

>>>>

As it can be seen from the output, to the variable `term` is not assigned the 
result of the calculation, yet an R\ call [see, e.g., @Wickham2019, for details 
on "non-standard evaluation"], which can eventually be evaluated with `eval()`,
